### 2014-06-06 abstract.tex
td comment in abs and minor corrections in intro

%!TEX root=paper.tex
\begin{abstract}
Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.
The first point is doing bottom-up Region of Interest (ROI) proposals instead of sliding-window evaluation.
The second point is using multi-layer Convolutional Neural Nets (CNNs) pre-trained on large-scale classification data to featurize canonically resized ROIs.
Although state of the art in recognition performance, the method is computationally costly, requiring CNN processing of upwards of two thousand regions.
Even with efficient GPU implementation, the method takes \textasciitilde 10 s per image after the computation of region proposals.% (another \textasciitilde 2 s).

>>>>

%!TEX root=paper.tex
\begin{abstract}
{\bf TD: this para reads awkward and a bit arrogant to me; can we replace with one crisp and strong sentance?  I also hate two paragraph abstracts.}
Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.
The first point is doing bottom-up Region of Interest (ROI) proposals instead of sliding-window evaluation.
The second point is using multi-layer Convolutional Neural Nets (CNNs) pre-trained on large-scale classification data to featurize canonically resized ROIs.
Although state of the art in recognition performance, the method is computationally costly, requiring CNN processing of upwards of two thousand regions.
Even with efficient GPU implementation, the method takes \textasciitilde 10 s per image after the computation of region proposals.% (another \textasciitilde 2 s).

### 2014-06-06 introduction.tex
td comment in abs and minor corrections in intro

Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
Overfeat overcomes this by incrementally computing the convnet features in overlapping windows, but then restricts the window locations to be on a relatively regular grid. RCNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
While RCNN has leading performance on PASCAL and ImageNet Detection as of the date of this writing, it is rather slow, at XXs per image.

Existing detection schemes, including RCNN and Overfeat, are generally relatively naive in terms of the temporal properties of their inference.
They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
(Or when time is considered a costly resource).
We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.

>>>>

Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
OverFeat \cite{Sermanet-ICLR-2014} overcomes this by incrementally computing the convnet features in overlapping windows, but then restricts the window locations to be on a relatively regular grid. RCNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
While RCNN has leading performance on PASCAL and ImageNet Detection as of the date of this writing, it is rather slow, at XXs per image.

Existing detection schemes, including RCNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
(Or when time is considered a costly resource).
We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.
